\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-18 article.tex
Added set theory and intro on methods

  They are \emph{non-hierarchical} and \emph{inclusive}, which is to say that
  an object can be associated with a great variety of tags
  simultaneously\cite{golder:ct}. The \emph{descriptive terms},
  \emph{keywords} or \emph{labels} are metadata connected to a given object
  which describe a concept or type of information\cite{heymann:ccch}.

@@

  Tagging is the act of organizing a collection of objects into related
  groups\cite{shirky:ontology}.

% Why do we tag?
%   this kind of metadata helps describe an item
%   allows it to be found again by searching
%   future navigation, filtering or search
%   later retrieval
%   categorize content using keywords
%   grouping related objects
%   classifies
%   organize
%   for the purpose of classification and retrieval
%   display venn diagram
%   explain venn diagram
% How do we tag (tagging)?
%   define tagging

% end the section with something like..
% tags add metadata to an object
% tagging groups objects
% the reason for why we bother is because we want to find the objects again

\SubSection{Retrieval}

% explain how later retrieval is done by using the venn diagram

@@

\Section{Method}
  Write introduction.

% Three parts
%   1. terminology (sonkal.taekwondo.cz)
%   2. english description (condensed encyclopedia)
%   3. tagging (how is tagging used? what is its role?)

@@

\SubSection{Approach}
% collecting data

@@

  % Thanks to Master Nicolaisen for pointing out that I allredy had found a
  % problem statement when I was still looking for one
  %
  % Odd-Magne Hansen for helping me with the terminology, and general feedback
  Todo.

>>>>

  They are \emph{non-hierarchical} and \emph{inclusive}, which is to say that
  an object can be associated with a great variety of tags
  simultaneously\cite{golder:ct}. The \emph{descriptive terms},
  \emph{keywords} or \emph{labels} are metadata connected to a given object
  that describes a concept or type of information\cite{heymann:ccch}.

@@

  \emph{Tagging} is the act of organizing a collection of objects into related
  groups\cite{shirky:ontology}.

\SubSection{Set theory}

  The characteristics of tags make them excellent for future navigation,
  filtering or search. An object which has been tagged contains a collection,
  or a set, of tags.  Each tag is an element of the set. The order of elements
  within the set is irrelevant, but each element can only occur once.

  For example, $\{1,5,8\}$ denotes a set with three elements: 1, 5 and 8.
  $\{5,8,1\}$ is the same set, since the order of the elements doesn't matter.
  $\{1,1,1\}$, however, is not a valid set because the element 1 occurs
  several times. Elements in a set can also contain strings, so $\{loons,
  penguins, terns\}$ is a valid set.

% set operations

% union, intersection

@@

\Section{Method}

  In this section we describe where the data originates, and then elaborate on
  the approach taken to register and investigate the dataset.

@@

\SubSection{Approach}
% collecting data into text files
% tagging (how is tagging used? what is its role?)

@@

  % Thanks to Master Nicolaisen (VII. Dan) for pointing out that I already had
  % found a problem statement when I was still looking for one
  %
  % Odd-Magne Hansen (III. Dan) for helping me with the terminology, and
  % general feedback
  Todo.
